% resume.tex
%
% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003 David J. Grant <dgrant@ieee.org> http://www.davidgrant.ca
% (c) 2007 Todd C. Miller <Todd.Miller@courtesan.com> http://www.courtesan.com/todd
% (c) 2009-2012 Derek R. Hildreth <derek@derekhildreth.com> http://www.derekhildreth.com
%This work is licensed under the Creative Commons Attribution-NonCommercial-ShareAlike License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/1.0/ or send a letter to Creative Commons, 559 Nathan Abbott Way, Stanford, California 94305, USA.

% GENERAL NOTE:  There may be some notes specific to myself.  If you're only interested in my LaTeX source or it doesn't make sense, please disregard it.

\documentclass[letterpaper,11pt]{article}

%-----------------------------------------------------------
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage[pdftex]{hyperref}
\hypersetup{
colorlinks,%
citecolor=black,%
filecolor=black,%
linkcolor=black,%
urlcolor=black
%urlcolor=mygreylink     % can put red here to better visualize the links
}
\urlstyle{same}
\definecolor{mygrey}{gray}{.85}
\definecolor{mygreylink}{gray}{.40}
\textheight=9.0in
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{0.375in}
\addtolength{\textwidth}{0.5in}
\addtolength{\topmargin}{-.375in}
\addtolength{\textheight}{0.75in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resitemskills}[1]{\item #1 \vspace{-4pt}}
\newcommand{\resheading}[1]{{\large \colorbox{mygrey}{\begin{minipage}{\textwidth}{\textbf{#1 \vphantom{p\^{E}}}}\end{minipage}}}}
\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingproj}[4]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubsubheading}[2]{
\begin{tabular*}{6.5in}{l@{\extracolsep{\fill}}r}
    \textit{#1} & \textit{#2} \\
\end{tabular*}\vspace{-6pt}}
%-----------------------------------------------------------

%-----------------------------------------------------------
%General Resume Tips
%   No periods!  Technically, nothing in this document is a full sentence.
%   Use parallelism by ending key words with the same thing,  i.e. "Coordinated; Designed; Communicated".
%   More tips on bottom of this LaTeX document.
%-----------------------------------------------------------

\begin{document}

    \centering\textbf{\huge Wenlin (Jeremy) Huang}\\ \vspace{0.1in}

    (650) 567-6624, \href{mailto:huang.wenl@husky.neu.edu}{huang.wenl@husky.neu.edu}, {W Mercer Street, Seattle, WA 98119} \\

    {Available for Internship/Co-op: \textbf{\underline{Jan. - Aug. 2018}}}

    % CHANGE HEADER SOURCE HERE

    %%%%%%%%%%%%%%%%%%%%%%
    \resheading{Education}
    \begin{itemize}
        % Education #1
        \item[]
        \ressubheading{\href{http://www.northeastern.edu/seattle/}{Northeastern University - Seattle}}{Seattle, WA}{Master of Science in Computer Science} {Sept. 2016 -- Dec. 2018 (Expected)}
        { \footnotesize
        \begin{itemize}
            \resitem{\textbf{Key Courses: }MEAN Stack Web Development, Algorithms, Object-oriented Design}

        \end{itemize}
        }

        % Education #2
        \item[]
        \ressubheading{\href{http://www.shnu.edu.cn/}{Shanghai Normal University}}{Shanghai, China}
        {Bachelor of Business Administration in E-Commerce}{Sept. 2011 -- Jul. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{\textbf{Key Courses: }Algorithms and Data Structures, Database Systems}

            % \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1045.htm}{Computer Architecture}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1073.htm}{Data Communications}, ¥\href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1072.htm}{Real-Time and Embedded Systems}, \href{http://derekhildreth.com/portfolio/Resume/catalog/class.asp1069.htm}{Digital Systems Design}}
        \end{itemize}
        }
    \end{itemize} % End Education list

    %%%%%%%%%%%%%%%%%%%%%%



    %%%%%%%%%%%%%%%%%%%%%%
    \resheading{Technical Skills}
    \begin{itemize}
        \item
        {\bf Programming Languages:}
        \vspace{-0.2cm} Java (Proficient), JavaScript (Intermediate), Ruby, Python, Racket

        \item
        {\bf Frameworks and Tools:}
        \vspace{-0cm} Bootstrap, jQuery, AngularJS 1.x, Node/Express.js, Ruby on Rails, Git

        %     	\item
        %           \resitemskills {\footnotesize {\bf Programming Languages:}
        %               \hspace{0.4cm}  Java (Proficient), Ruby, JavaScript, Python, C, Racket
        %           }
        % 		\item
        %           \resitemskills{\footnotesize {\bf Front-end technologies:}
        %               \hspace{0.75cm}  CSS, Bootstrap, jQuery, AngularJS
        %           }
        %         \item
        %           \resitemskills{\footnotesize {\bf Back-end technologies:}
        %               \hspace{0.86cm}  Ruby on Rails, Node.js, Spring MVC
        %           }
        %         \item
        %           \resitemskills{\footnotesize {\bf Operating Systems:}
        %               \hspace{1.35cm}  macOS, Ubuntu, Windows
        %           }
    \end{itemize}
    %%%%%%%%%%%%%%%%%%%%%%
    % Would have completed this if I had not had all projects listed under "Skills".
    % Still a good idea.  See if I can fit it in somewhere...  Otherwise, just print it out and bring it to an interview if needed.
    %%%%%%%%%%%%%%%%%%%%%%

    % \begin{description}

    % 					\resitem{\textbf{\href{http://www.byui.edu/Societies/Linux/}{:}}}
    % 						\begin{itemize}

    % 						\end{itemize}
    % \end{description}






    % --------------------  Projects --------------------%
    % \resheading{\href{http://www.derekhildreth.com/portfolio.php}{Projects}}
    \resheading{Academic Projects}

    % --------------------  Project 0 --------------------%
    \begin{itemize}
        \item
        \ressubheadingproj
        {\href
        {https://github.com/jeremylinlin/tic-tac-toe-mean}
        {Multiplayer Tic-Tac-Toe Platform {\normalfont (Northeastern Univ.)}}
        }
        {Jul. 2017 -- Aug. 2017}
        {Web Development Intern}{Jun. 2015 -- Oct. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{Developed an online Tic-Tac-Toe platform using the MEAN Stack that allows users to play with either the computer or another player online}
            % 					\resitem{Implemented the website frond end with AngularJS and created RESTful API endpoints with Node.js, and used MongoDB for data storage}
            \resitem{Incorporated Socket IO into the project which enables real-time communications between multiple connected clients in an online game}
            \resitem{Used Facebook/Google Sign-in services for social login and consumed a third-party Tic-Tac-Toe API for recommendations of computer moves}
        \end{itemize}

        }
    \end{itemize}

    % --------------------  Project 1 --------------------%
    \begin{itemize}
        \item
        \ressubheadingproj{Space Invaders {\normalfont (Northeastern Univ.)}}{Oct. 2016 -- Nov. 2016}
        {Web Development Intern}{Nov. 2014 -- Mar. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{Designed and developed the data structures and features of the game in Racket by applying the design recipe}
            \resitem{Refactored and further extended the game by intensively using higher-order functions}
            \resitem{Created unit tests with 100\% code coverage}

        \end{itemize}
        }
    \end{itemize}
    % --------------------  Project 2 --------------------%
    \begin{itemize}
        \item
        \ressubheadingproj{Algorithms Course Projects {\normalfont (Coursera)}}{Feb. 2016 -- Apr. 2016}
        {Web Development Intern}{Nov. 2014 -- Mar. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{Established a computational model to estimate the value of the percolation threshold via Monte Carlo simulation using the Union-Find Algorithm}
            \resitem{Implemented an efficient, sorting-based algorithm to find every line segment that connects a subset of 4 or more of the points in the plane}
            \resitem{Developed a solution to the 8-puzzle problem using the A* search algorithm}
            \resitem{Designed a data type that represents a set of points in a unit square using a 2d-tree to support efficient range
            search and nearest-neighbor search}
        \end{itemize}
        }
    \end{itemize}

    \resheading{Experience}
    \begin{itemize}
        \item  % SAP Labs
        \ressubheading{SAP Labs China}{Shanghai, China}
        {Web Development Intern}{Jun. 2015 -- Oct. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{Worked in SAP Jam Department in the hybris-community integration team}
            \resitem{Used Spring Framework and later switched to JavaScript to fetch reviews and ratings information from an E-commerce community, and integrated them as add-ons on hybris Commerce Suite}
            \resitem{Integrated Apache Solr into the project for better search performance}
            \resitem{Fixed various bugs and cross-browser compatibility issues during development and integration process}
        \end{itemize}
        }

        \item % VSC China
        \ressubheading{\href{http://www.vsc.com}{Venus Software Corporation}}{Shanghai, China}{Web Development Intern}{Oct. 2014 -- Jan. 2015}
        { \footnotesize
        \begin{itemize}
            \resitem{Designed and developed a WeChat news pulling/pushing system with Spring MVC
            and Hibernate, and a mobile-friendly news feed with jQuery Mobile}
            \resitem{Participated in the development of an EDM (Email Direct Marketing) system using
            Ruby on Rails}
        \end{itemize}
        }

    \end{itemize}  % End Experience list



    % \item[Pydom:] { \footnotesize Pydom scans through a list of web pages, grabs the HTML source, and parses interactive elements. These interactive elements written to an XML catalog which is used as the main input for a Selenium .Net project.}

    % \item[Xerrscrape:] { \footnotesize Used to fill a missing area of product testing, this Python program scans through all XML error logs on the specified server, tallies errors collectively, and sends notifications when an error occurs more than the threshold.}

    % \item[.Net CWS Test API:] { \footnotesize This framework provides automated testing for RightNow Connect Web Services for SOAP (.Net Toolkit).  Using reflection, objects and NUnit tests are instantiated based on JSON input.}
    % \item[\href{https://bitbucket.org/dhildreth/canon\_webview}{Canon Webcam API}:] {\footnotesize Allows programmatic authentication and control for Canon 360$^\circ$ Webcams in Python.}
    % \end{description} % end description already Copied to above

\end{document}


\newpage
\myheader
\resheading{Hardware Engineering Projects} % If printed as a seperate page, get more detailed in the descriptions!  What type of processor?  What program used? Etc.

\begin{description}
    \item[4 and 8 bit RISC CPUs] {\footnotesize Simple CPUs designed using CircuitMaker (no HDL) which contained ALUs, counters, registers, and 1K RAM all designed from scratch}
    \item[Simple Calculator] {\footnotesize Designed a simple calculator from the ground up using Xilinx ISE and Verilog HDL} % Get schematic block diagram for this one!
    \item[Stereo Amplifier] {\footnotesize Contained I/O as well as bass, treble, and volume controls}
    \item[Power Supply Basics] {\footnotesize Learned about the very basics of power supply design using transformers, rectifiers, and zener diodes and voltage regulators.}
    \item[Parallel Port Game Controller] {\footnotesize Went through the start to finish development process of a game controller including driver development, microprocessor  \& ADC design (8255 MicroBoard; N.I.	ADC0809), and PCB design}
    \item[Portable Microphone Amplifier] {\footnotesize Utilized a series of transistors to amplify sound in a room with a potentiometer as volume control}
    \item[MP3 Player] {\footnotesize Developed an MP3 player using the Analog Devices BlackFin BF533 microprocessor and EZ-KIT development kit which utilized interrupts and audio codec}  % get link to block diagram for this one!
    \item[INL Remote Cell Phone Control] {\footnotesize Senior project which developed a prototype for Idaho National Laboratories allowing them to remote control a cell phone via 802.11g and bluetooth at a range greater than 6000ft consisting of 3 major components: central control, wireless medium, and embedded systems for chuckar box}
    \item[Inverted Pendulum] {\footnotesize Used sliding mode feedback control and inverted pendulum kit to keep metal rod standing vertially on a swingin arm}
    \item[FM Transmitter] {\footnotesize Built a simple FM Transmitter based off of given schematics as an introduction to FM modulation signals}
\end{description}


\resheading{Software Engineering Projects}  % There really are a TON of projects I can put on this, but here are some major ones:
\begin{description}
    \item[Book Keyword Scanner] {\footnotesize Developed a program which will take any input file and, given a keyword search, will return the frequency of that word }
    \item[Pedigree Chart] {\footnotesize Developed a program which will parse through a pedigree file and display a pedigree chart in the command line}
    \item[Factory Nail Rejection] {\footnotesize This program was simulating a factory which produced nails that had to be a very specific length, and if it wasn't, the program would reject it}
    \item[Calendar Program] {\footnotesize Given the time and date to display, the calendar program would display a simple calendar on the command line which took into account leap years}
    \item[Normal Distribution] {\footnotesize This program simulated the classic wheel of fortune blinko game where several thousand chip were statistially recorded and displayed as they dropped into a board filled with pegs}
    \item[RSA Encryption] {\footnotesize Developed an application which utilized the RSA encryption method to encrypt and decrypt messages}
\end{description}

\end{document}

%Only Print References If Requested!  Maybe even put it in it's own page.  Must have same heading as first page.
%%%%%%%%%%%%%%%%%%%%%%
\newpage
\myheader
\resheading{References}
\begin{center}
\begin{tabular*}{1\textwidth}{@{\extracolsep{\fill}}  l l l }
Toby Rummans & Eric Karl & Gordon Smith \\
Entry Level Web Developer & Computer Science \& Engineering  & Technology Support Specialist \\
\vspace{10pt}
Memolinkcorp & BYU-Idaho & BYU-Idaho \\
[removed] & 525 South Center St. & 525 South Center St.  \\
Denver, CO 80210 & Rexburg ID 83460 & Rexburg ID 83460 \\
[removed] & (208) 496-3097 & (208) 496-2816 \\
\end{tabular*}
\end{center}

% \end{document}


% ADDITIONAL WORK EXPERIENCE NOT INCLUDED	OR OLD

\item
\ressubheading{\href{http://www.rexburgmotorsports.com/}{Rexburg Motorsports}}{Rexburg, ID}{Computer Systems Administrator}{Aug. 2006 -- Oct. 2006}
{ \footnotesize
\begin{itemize}
\resitem{Managed file and application servers running Windows 2003 Server}
\resitem{Performed all levels of hardware and software systems support for 40 computers and 10 printers}
\end{itemize}
}

\item
\ressubheading{Bresnan Communications}{Billings, MT}{Teir 1 Technical Support}{Jan. 2006 -- April 2006}
{ \footnotesize
\begin{itemize}
\resitem{Provided Bresnan customers with technical support over the phone.}
\resitem{Receieved training on resolving networking, cable TV, and VOIP issues.}
\end{itemize}
}

\item
\ressubheading{Northwestern Energy}{Billings, MT}{Summer Gas/Electrical Engineer}{May 2004 -- April 2005}
\begin{itemize}
\resitem{Interned with full time Gas/Electrical Engineers.}
\resitem{Documented, mapped, and marked city streetlights using MS Access, GTViewer, FRAMME, and CAD.}
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%
% GENERAL RESUME NOTES %
%%%%%%%%%%%%%%%%%%%%%%%%
Need to brush up on the skills section?  Here are some really good ideas:

- Communication: The ability to express and interpret ideas and convey knowledge.
Skills like speaking effectively, writing concisely, listening attentively, expressing ideas,
reporting information, editing, interviewing, and facilitating group discussion.

- Research and Planning: The ability to search for specific knowledge and formulate a
program for a definite course of action. Skills like forecasting, predicting, identifying
issues, finding alternatives, gathering information, solving problems, setting goals,
extracting information, and developing strategies.

- Human Relations: The ability to apply interpersonal skills to resolve conflict, relate to
people, and help people. Skills like providing support for others, listening, delegating
with respect, representing others, asserting, developing rapport, and perceiving
feelings.

- Management, Organization, Leadership: The ability to supervise others and guide
individuals and groups towards the completion of tasks. Skills like managing groups,
selling ideas, making decisions, managing conflict, coordinating tasks, teaching,
enlisting help.

Source:
http://www.squawkfox.com/2009/03/08/6-action-words-that-make-your-resume-rock/

Other Resources:
http://www.tvmier.com/Resume_Education.html

